### 2023-01-18 paper-reviews/papers-2023.tex
Add ARM Helios article

    \cite{Gwennap:ARM-Neoverse:2019}.
\end{itemize}

>>>>

    \cite{Gwennap:ARM-Neoverse:2019}.

    \item The article describes ARM 64-bit only architecture called Helios. It is a first licensable CPU that combines OOO and multithreaded execution. The main application for the processor are data transfer infrastructure and automotive industry. The processor architecture supports INT8 and FP16 formats that are the current trend for DNN acceleration. On top of INT8 and FP16 the processor can be closes integrated with various accelerators:

    \cite{Demler:Helios:2019}
\end{itemize}
